---
title: "Application of statistical modeling for conventional and social media movies "
date: "12/23/2019"
output: word_document
editor_options: 
  chunk_output_type: inline
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readr)
csm <- read.csv(choose.files())
library(ggplot2)
library(dplyr)
#The main objective of this project is to explore and create a linear Regression Model so as to try to predict the Movies in demand.
str(csm)
head(csm)
```

## Data Exploration

```{r}
#CHECKING MISSING VALUES:
#install.packages("pastecs")
library(pastecs)
summary(csm)

#To find stat values (total n, number of null values, number of na's, Mean, Median Min, MAx etc)
stat.desc(csm)

#To find duplicate rows
sum(duplicated(csm))

# There are no duplicate rows in the dataset.
```

## Checking the distribution of each variables before data cleaning.

```{r}
hist(csm$Budget, breaks=15, xlab = "Budget", main = "Historgram of Budget",col="green")

hist(csm$Ratings, breaks=15, xlab = "Ratings", main = "Historgram of Ratings",col="blue")

hist(csm$Likes, breaks=15, xlab = "Likes", main = "Historgram of Likes",col="red")

hist(csm$Dislikes, breaks=15, xlab = "Dislikes", main = "Historgram of Dislikes",col="yellow")

hist(csm$Views, breaks=15, xlab = "Views", main = "Historgram of Views",col="brown")
```

## Data Cleaning:

```{r}
#Dealing with missing values and error data
#To find NA values
colSums(is.na(csm))

#Heat map to visualize missing values
library(VIM)
missing.values <- aggr(csm, sortVars = T, prop = T, sortCombs = T, cex.lab = 1.5, cex.axis = .6, cex.numbers = 5, combined = F, gap = -.2)

#To check complete cases in the dataset
sum(complete.cases(csm))

#187 rows are coomplete cases, 44 rows does have missing values.

#Does my data have any missing value
apply(csm,2,function(x) sum(is.na(x)))

# There are missing values or NA's in our dataset.(budget-1,screens-10,aggr.followers-35)

#Now, let’s use apply() function to get percent missing by rows:
percentmiss = function(x){sum(is.na(x))/length(x)*100}
missing <- apply(csm,1,percentmiss)
table(missing)

#To subset the bad rows out
replace = subset(csm, missing <= 5)
missing1 = apply(replace,1,percentmiss)
table(missing1)

dont = subset(csm, missing > 5)
missing2 = apply(dont,1,percentmiss)
table(missing2)

apply(csm,2,percentmiss)

#Figuring out the columns to be excluded
replace_col = replace[,-c(1,2)]
dont_col = replace[,c(1,2)]

#USing Mice to know what and how to replace the data
library(mice)
temp_no_miss = mice(replace_col)

no_miss = complete(temp_no_miss,1)
summary(no_miss)

#Putting everything back together
all_col = cbind(dont_col, no_miss)
summary(all_col)

all_rows = rbind(dont, all_col)
summary(all_rows)

```

#DOes our data have any outliers?

```{r}
##OUTLIERS 

select_cols <- all_rows[ ,-c(1,2)]

mahal = mahalanobis(select_cols,
                    colMeans(select_cols, na.rm=TRUE),
                    cov(select_cols, use ="pairwise.complete.obs"),
                    tol=1e-20
)

summary(mahal)

#Find the cutoff score to deal with outliers

cutoff = qchisq(1-.001,ncol(select_cols))
print(cutoff)

summary(mahal < cutoff)

cor_data = subset(all_rows, mahal < cutoff)
str(cor_data)

```

## Assumption:

# 1. Additivity:

```{r}
cor(cor_data[,-c(1,2)])

library(corrplot)

corrplot(cor(cor_data[,-c(1,2)]))
symnum(cor(cor_data[,-c(1,2)]))

```

# Assumption: If you have several predictors then their combined effect is best described by adding their effects together. Look for a B ,*

# Observation: It has no B and *. but it has the correlation coefficient as 0.8 (+) which is somewhat closer to 1 and slightly high correlation. We can conclude that the assumption is not met for additivity.

# 2. Linearity:

```{r}
random = rchisq(nrow(cor_data[,-c(1,2)]), 11)
fake = lm(random~., data = cor_data[,-c(1,2)])
summary(fake)

standardized = rstudent(fake)
qqnorm(standardized)
abline(0,1)

```
# Assumption: The relationship between the variables should be linear and the line should not be curved.

# Observation: The line is not curved and it denotes the linear relationship among the variables.

# 3. Normality:

```{r}
hist(standardized, breaks = 15)
```

# Assumption: All the linear combinations of the variables need to be normal.

# Observation: The curve is not normal, looks like skewed to the right, so we can say that the assumption is not met.

## 4. Homogeneity and Homoscedesticity:

```{r}

fitvalues = scale(fake$fitted.values)
plot(fitvalues, standardized) 
abline(0,0)
abline(v = 0)

plot(fake,1)
```

# Assumption: 
For Homogeniety, the spread above the line should be same as below that 0, 0 line.
For Homoscedesticity, the spread should be equal all the way across the x axis

# Observation: 
Yes, They are evenly spread above and below the line and Based on the spread above and below the line, the homogeneity of the variances cannot be rejected.
Yes, Since the points are random and the line looks approximately flat, we can accept the homoscedasticity

## HYPOTHESIS TESTING:

#1.The budget of the movies does have an impact on the popularity of the film.

```{r}
hypo_check1 <- lm(cor_data$Ratings~cor_data$Budget)
summary(hypo_check1)

t.test(cor_data$Ratings, cor_data$Budget, var.equal = TRUE)
```

# Observation: Since the p value (0.0001) is too small which is less than 0.05, we can conclude that we can reject the null hypothesis and say that the popularity of the film is not impacted by the budget of the movie.

# 2. There is no relationship between the likes/dislikes of the movies and the rating of the movies.

```{r}
hypo_check2 <- lm(cor_data$Ratings~cor_data$Likes + cor_data$Dislikes)
summary(hypo_check2)

t.test(cor_data$Ratings, cor_data$Likes + cor_data$Dislikes, var.equal = TRUE)
```
# Observation: Since the p-value is less than 0.05, we can reject the null hypothesis, hence The likes/dislikes of the movie determines the rating of the movies.

## Data Visualization:

#HISTOGRAMS to check the Normality and data distribution. 
#----------
```{r}
hist(cor_data$Budget, breaks=15, xlab = "Budget", main = "Historgram of Budget",col="green")
# This distribution is Right Skewed meaning there are values that are higher than the mean. Outliers are present.

hist(cor_data$Ratings, breaks=15, xlab = "Ratings", main = "Historgram of Ratings",col="blue")
# This distribution is almost Normal distribution and there are no outliers.

hist(cor_data$Likes, breaks=15, xlab = "Likes", main = "Historgram of Likes",col="red")
# This distribution is Right Skewed meaning there are values that are higher than the mean. There are no outliers.

hist(cor_data$Dislikes, breaks=15, xlab = "Dislikes", main = "Historgram of Dislikes",col="yellow")
# This distribution is Right Skewed meaning there are values that are higher than the mean. There are no outliers.

hist(cor_data$Views, breaks=15, xlab = "Views", main = "Historgram of Views",col="brown")
# This distribution is Right Skewed meaning there are values that are higher than the mean. Outliers are present.

```

#SCATTERPLOTS
#------------
```{r}
cleanup = theme(panel.grid.major = element_blank(),
                panel.grid.minor = element_blank(),
                panel.background = element_blank(),
                axis.line.x = element_line(color = 'black'),
                axis.line.y = element_line(color = 'black'),
                legend.key = element_rect(fill = 'white'),
                text = element_text(size = 15))

#Scatter Plot to show the relationship between budget and movie ratings
ggplot(data = cor_data, aes(Budget,Ratings)) + geom_point(alpha = 0.3, aes(color = Ratings)) + theme_bw()

#The above scatterplot shows that the least the budget of the movies is, the better the ratings are.

#Scatter Plot to show the relationship between Likes (number of total #likes) and movie ratings.
ggplot(data = cor_data, aes(Likes,Ratings)) + geom_point(alpha = 1.0, aes(color = Ratings)) + theme_bw()

#The above graph shows higher ratings of movies have lesser likes.


#Scatter Plot to show the relationship between dislikes (number of total #likes) and movie ratings.
ggplot(data = cor_data, aes(Dislikes,Ratings)) + geom_point(alpha = 1.0, aes(color = Ratings)) + theme_bw()

#The above graph shows higher ratings of movies have lesser Dislikes too. 

scatter = ggplot(cor_data, aes(Views, Ratings))
scatter +
  geom_point() +
  geom_smooth(method="lm") +
  xlab("Movie Views") +
  ylab("Ratings") +
  cleanup

#Budget vs Ratings Scatterplot:
scatter = ggplot(cor_data, aes(Budget, Ratings))
scatter +
  geom_point() +
  geom_smooth(method="lm") +
  xlab("Budget") +
  ylab("Ratings") +
  cleanup

#Anlaysis 1-
#From the above obsevation, we can conclude that there is no relation between likes/dislikes and the ratings of the movie.

```

# Linear Regression - BiVariate Analysis 
```{r}
head(cor_data)

#We hypothesized that Likes and Dislikes determine the popularity of a movie and Budget doesn't have any impact. Investigating relationships between Ratings and each of the Numerical Variables
#Ratings vs Likes
plot(cor_data$Ratings ~ cor_data$Likes, main="Ratings vs Likes", xlab="Likes", ylab="Ratings")
m1 <- lm( Ratings ~ Likes,data = cor_data)
abline(m1)
summary(m1)
r1=cor(cor_data$Ratings, cor_data$Likes)
r1
res1=sum(m1$residuals^2)
res1

#Ratings vs Dislikes
plot(cor_data$Ratings ~ cor_data$Dislikes, main="Ratings vs Dislikes", xlab="Dislikes", ylab="Ratings")
m2 <- lm( Ratings ~ Dislikes,data = cor_data)
abline(m2)
summary(m2)
r2=cor(cor_data$Ratings, cor_data$Dislikes)
r2
res2=sum(m2$residuals^2)
res2

#Ratings vs Budget
plot(cor_data$Ratings ~ cor_data$Budget, main="Ratings vs Budget", xlab="Budget", ylab="Ratings")
m3 <- lm( Ratings ~ Budget,data = cor_data)
abline(m3)
summary(m3)
r3=cor(cor_data$Ratings, cor_data$Budget)
r3
res3=sum(m3$residuals^2)
res3

#Ratings vs Views
plot(cor_data$Ratings ~ cor_data$Views, main="Ratings vs Views", xlab="Views", ylab="Ratings")
m4 <- lm( Ratings ~ Views,data = cor_data)
abline(m4)
summary(m4)
r4=cor(cor_data$Ratings, cor_data$Views)
r4
res4=sum(m4$residuals^2)
res4

#Ratings vs Screens
plot(cor_data$Ratings ~ cor_data$Screens, main="Ratings vs Screens", xlab="Screens", ylab="Ratings")
m5 <- lm( Ratings ~ Screens,data = cor_data)
abline(m5)
summary(m5)
r5=cor(cor_data$Ratings, cor_data$Screens)
r5
res5=sum(m5$residuals^2)
res5

#Ratings vs Comments
plot(cor_data$Ratings ~ cor_data$Comments, main="Ratings vs Comments", xlab="Comments", ylab="Ratings")
m6 <- lm( Ratings ~ Comments,data = cor_data)
abline(m6)
summary(m6)
r6=cor(cor_data$Ratings, cor_data$Comments)
r6
res6=sum(m6$residuals^2)
res6

#Ratings vs Gross
plot(cor_data$Ratings ~ cor_data$Comments, main="Ratings vs Gross", xlab="Gross", ylab="Ratings")
m7 <- lm( Ratings ~ Gross,data = cor_data)
abline(m7)
summary(m7)
r7=cor(cor_data$Ratings, cor_data$Gross)
r7
res7=sum(m7$residuals^2)
res7

#Ratings vs Aggregate Followers
plot(cor_data$Ratings ~ cor_data$Aggregate.Followers, main="Ratings vs Aggregate Followers", xlab="Aggregate Followers", ylab="Ratings")
m8 <- lm( Ratings ~ Aggregate.Followers,data = cor_data)
abline(m8)
summary(m8)
r8=cor(cor_data$Ratings, cor_data$Aggregate.Followers)
r8
res8=sum(m8$residuals^2)
res8


#From the bivariate analysis, we observe that Likes is not a good predictor for Ratings since R2 value is very less (<1%). Similar case with Views, Screens, Comments and Aggregate Followers. Dislikes, Budget and Gross indicates looks like significant predictors of popularity since pvalue is less than 0.05 even though R value is less.
```

## CHOOSING THE BEST MODEL

# 1. Backward Elimination (p-value approach)

```{r, qbest}

#m9 <-lm(Ratings ~ Likes + Dislikes, data=cor_data)
#summary(m9)

m_all <- lm( Ratings ~ Aggregate.Followers + Gross + Budget + Likes + Comments + Screens + Dislikes + Views, data = cor_data)
summary(m_all)

m_all_1 <- lm( Ratings ~ Aggregate.Followers + Gross + Likes + Comments + Screens + Dislikes + Views, data = cor_data)
summary(m_all_1)

m_all_2 <- lm( Ratings ~ Gross + Likes + Comments + Screens + Dislikes + Views, data = cor_data)
summary(m_all_2)

m_all_3 <- lm( Ratings ~ Gross + Likes + Screens + Dislikes + Views, data = cor_data)
summary(m_all_3)

m_all_4 <- lm( Ratings ~ Gross + Likes + Dislikes + Views, data = cor_data)
summary(m_all_4)

```

#m_all_4 is the best model as p values are less than 0.05
#y = 6.066 + 5.247*10^-9*(Gross) +  2.77*10^-5*(Likes) - 1.047*10^-3*(Dislikes) + 8.63*10^-8*(Views)
#35.28% Variability in the Rating Score or Popularity is explained by the model
#A movie with a million USD Gross, 10000 Likes and 500 Dislikes and with 100k Views is likely to get a rating of 6.066+0.0052+0.277-0.524+0.00863 = 5.83283

# 2. Backward Elimination (R2adj approach)

```{r}
mr2adj_all <- lm( Ratings ~ Aggregate.Followers + Gross + Budget + Likes + Comments + Screens + Dislikes + Views, data = cor_data)
summary(mr2adj_all)

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Budget + Likes + Comments + Screens + Dislikes, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Budget + Likes + Comments + Screens + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Budget + Likes + Comments + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Budget + Likes + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Budget + Comments + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Likes + Comments + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Budget + Likes + Comments + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~  Gross + Budget + Likes + Comments + Screens + Dislikes + Views, data = cor_data))

mr2adj_all_1_best <- lm( Ratings ~ Aggregate.Followers + Gross + Likes + Comments + Screens + Dislikes + Views, data = cor_data)
summary(mr2adj_all_1_best)

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Likes + Comments + Screens + Dislikes, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Likes + Comments + Screens + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Likes + Comments + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Likes + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Gross + Comments + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Aggregate.Followers + Likes + Comments + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Gross + Likes + Comments + Screens + Dislikes + Views, data = cor_data))

mr2adj_all_2 <- lm( Ratings ~ Gross + Likes + Comments + Screens + Dislikes + Views, data = cor_data)
summary(mr2adj_all_2)

#summary(lm( Ratings ~ Gross + Likes + Comments + Screens + Dislikes, data = cor_data))

#summary(lm( Ratings ~ Gross + Likes + Comments + Screens + Views, data = cor_data))

#summary(lm( Ratings ~ Gross + Likes + Comments + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Gross + Likes + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Gross + Comments + Screens + Dislikes + Views, data = cor_data))

#summary(lm( Ratings ~ Likes + Comments + Screens + Dislikes + Views, data = cor_data))
```

# Comparing both the methods, We find that Likes, Dislikes, Views and Gross are overlap and Hence we will choose them in our Best Model

##MODEL DIAGNOSTICS FOR m_all_4 - BEST PREDICTOR FOR RATING

```{r, Diag}
#Linearity condition is reasonably met - Based on scatter plot and residuals plot below, we see that relationship between runs and new_obs can be accepted to be linear
plot(cor_data$Ratings ~ cor_data$Likes)
plot(cor_data$Ratings ~ cor_data$Dislikes)
plot(cor_data$Ratings ~ cor_data$Views)
plot(cor_data$Ratings ~ cor_data$Gross)

#Normality of residuals condition is met - normal qq plot is approximately a straight line with few steps in between which is due to discrete nature of the variables

hist(m_all_4$residuals, breaks=9)
qqnorm(m_all_4$residuals)
qqline(m_all_4$residuals)

#Constant Variability Condition is nearly met for Gross, Likes and Views- Variability of residuals around the 0 line is approximately same
plot(m_all_4$residuals ~ cor_data$Likes)
abline(h=0,lty=2)

plot(m_all_4$residuals ~ cor_data$Dislikes)
abline(h=0,lty=2)

plot(m_all_4$residuals ~ cor_data$Views)
abline(h=0,lty=2)

plot(m_all_4$residuals ~ cor_data$Gross)
abline(h=0,lty=2)

#Independence of Residuals is met
plot(m_all_4$residuals)
```
